---
title: "Hangout for R"
author: "Kuo,Yi-Chien"
date: "2019/5/6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##R Introduction
In addition to data processing and analysis, R has a complete operations for array and matrix and excellent graphical tools.Hence, R is also a fairly complete programming language.

##Basic Operator
The basic subject in R is vector. There are 6 main modes, logical, integer, double, single, complex, and character.

>Arithmetic Operator

```{r, echo=TRUE}
5*40
5+49
1/0
0/0
Inf -Inf
3^5
31%%2
31%/%2
```

------

**Example**
```{r, echo=TRUE}
intRate = 0.01
n = 10
principal = 1500
payment = principal * intRate /(1 - (1 + intRate)^(-n))
payment
```

------

##Objects
There are six types of subjects, vector, matrix, array, factor, list, data frame, function.

>Vector 

```{r, echo=TRUE}
x <- c(0,10,20)
x
x[-3]
seq(1,10,by=2) 
rep(1,10) 
```

------

**Example**  
```{r, echo=TRUE}
colors = c("brown","yellow","blue")
colors
paste(colors,"candy")  
paste0(colors,"candy")
substr(colors,2,4)
```

>Matrix

```{r, echo=TRUE}
m2=matrix(20:39,nrow=2,ncol=10,byrow=T)
m2
m2[2,5]
m2[2,]
m2[,10]
```

>Array

```{r, echo=TRUE}
array(1:120,c(5,4,3,2))
out=array(1:120,c(5,4,3,2))
out[,,2,2]
out[c(2,4),c(1,3),2,2]
```

>Data Frame

```{r, echo=TRUE}
color=c("red","red","red1","blue")
number=c(1,3,5,7)
logic=c(T,T,F,F)
out.fr=data.frame(colors=color,numbers=number,logics=logic)
out.fr
out.fr=data.frame(color,number,logics=logic)
out.fr
out.fr[,2] #Call by position
out.fr[,"number"] #call by name
out.fr$number #Call by name
```

##Common R Computing Functions

>Descriptive Statistics Functions

```{r, echo=TRUE}
x <- 10:31
x
mean(x)
var(x)
sum(x)
cumsum(x)
sd(x)
range(x)
fivenum(x)
```

>Functions for Characters

```{r, echo=TRUE}
paste("A", 1:5, sep = "")
paste("A", 1:5, sep = " ")
paste("A", 1:5, sep = "#") 
paste("Today is", date()) 
```

##R Graphics

```{r, echo=TRUE}
x1=(1:300)/100
x2=(301:600)/100
y1=3*x1+2
y2=2*x2-0.5*x2^2
plot(c(x1,x2),c(y1,y2),type="l")
```

------

**Example**  

```{r, echo=FALSE}
VADeaths

barplot(VADeaths, beside=TRUE, legend=TRUE, ylim=c(0,90),
 ylab="Deaths per 1000",
 main="Death rates in Virginia")

dotchart(VADeaths, xlim=c(0,75),
 xlab="Deaths per 1000",
 main="Death rate in Virginia")
```

------

**Example**  

```{r, echo=TRUE}
x <- rnorm(100)
hist(x, breaks=5)

D <- exp(rnorm(1000))
qqplot(x, D, main = "D is skewed to the right")
```

##R Programming Language

>Repetitive Execution

###for()
```{r, echo=TRUE}
fib=c(1,1)
golden_ratio <- c()
for (i in 3:20) {
  golden_ratio <- c(golden_ratio, fib[i-1]/fib[i-2])
  fib[i] <- fib[i-1]+fib[i-2]
  i=i+1 }
golden_ratio
```

------

###if()
```{r, echo=TRUE}
x=3
if(x>2) y=x^2 else y=cos(x)
y
x=1
if(x>2) y=x^2 else y=cos(x)
y
x=1
if(x==2) y=x^2 else y=cos(x)
y
x=1
if(x!=2) y=x^2 else y=cos(x)
y
```

------

###while()
```{r, echo=TRUE}
x <- 1
f <- x^3 + 2 * x^2 -7
tolerance <- 0.000001
while (abs(f) > tolerance){ 
 f.prime <- 3 * x^2 + 4 * x
 x <- x - f /f.prime
 f <- x^3 + 2 * x^2 -7
}
x
```

------

>Function Writing And Editing

```{r, echo=TRUE}
x = 10
g <- function() {
  x <- 10*x   #this changes g's local x not the one in f
return(x)
}
g()
```

------

>Probability and Random Number Generation

```{r, echo=TRUE}
random.number <- numeric(10)
random.seed <- 27218
for (j in 1:10) {
 random.seed <- (171*random.seed) %% 30269
 random.number[j] <- random.seed / 30269
}
random.number

runif(10)

runif(10,min=-3,max=10)

sample(1:100,size=10,replace=T)

sample(1:100,size=10,replace=F)

```

------

**Exercise**
```{r, echo=TRUE}
dbinom(x=4,size=6,prob=0.5)

pbinom(4,6,0.5)

qbinom(0.89,6,0.5)

rbinom(24,15,0.1)

```

------

**Exercise**
```{r, echo=TRUE}
set.seed(1)
T = -log(1-runif(10000))/1
EXP = rexp(10000,1)
par(mfrow=c(1,2)) #一頁有兩張圖片
hist(T,breaks=40)
hist(EXP,breaks=40)
```

##Linear Algebra

```{r, echo=TRUE}
cbind(seq(1,3),seq(2,4),seq(3,5))
1/cbind(seq(1,3),seq(2,4),seq(3,5)) 

X <- matrix(c(1,2,3,1,4,9),ncol=2)
X
X[,2]
X[,2,drop = FALSE]
class(X[,2]) #"numeric"
class(X[,2,drop = FALSE]) #"matrix"

X=as.data.frame(x)
X
X$x
```

------

**Exercise**
```{r, echo=TRUE}
H3 = matrix(c(1,1/2,1/3,1/2,1/3,1/4,1/3,1/4,1/5),nrow=3)
H3
svd(H3)
chol(H3)
chol2inv(H3)
solve(H3)
qr(H3)
qr.Q(qr(H3))
apply(H3,1,sum) #每一列加總 
apply(H3,2,sum) #每一行加總
```


------

**Linear Algebra**
```
t() #轉置矩陣
t()%*%y #%*% 矩陣內積
t() #轉置矩陣
det() #判別式 ad-bc
diag() #對角線
dim() #dimension of rows and columns
eigen(H)
eigen(H)$values
eigen(H)$vectors
```